### 2022-03-29 README.Rmd

1. Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
2. Arctic Marine Mammals Program, Alaska Department of Fish and Game, Fairbanks, Alaska, USA
3. Department of Wildlife Management, North Slope Borough, Utqiaġvik, Alaska, USA

@@

This repository serves as the research compendium in support of the above titled paper.
As the manuscript works its way through peer review and the publications process,
additional reproducibility features (e.g. Dockerfile, MyBinder.org) and
an R/Shiny application to explore results will be made available.

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered as a PDF,
    [London_HauloutBehavior.pdf](https://github.com/jmlondon/berchukHaulout/blob/main/analysis/paper/London_HauloutBeahvior.pdf), suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

  - [:file\_folder: data](/data): data used for model fits and final model output

>>>>

1. Marine Mammal Laboratory, Alaska Fisheries Science Center, National Marine Fisheries Service, NOAA, Seattle, Washington, USA
2. Arctic Marine Mammals Program, Alaska Department of Fish and Game, Fairbanks, Alaska, USA
3. Department of Wildlife Management, North Slope Borough, Utqiaġvik, Alaska, USA

@@

This repository serves as the research compendium in support of the above titled paper.
As the manuscript works its way through peer review and the publications process,
additional reproducibility features (e.g. Dockerfile, MyBinder.org) and
an R/Shiny application to explore results will be made developed and made available.

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered PDF,
    [London_HauloutBehavior.pdf](https://github.com/jmlondon/berchukHaulout/blob/main/analysis/paper/London_HauloutBeahvior.pdf), suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

  - [:file\_folder: data](/data): data used for model fits and final model output
  - [:file\folder: data_raw](/data_raw): data provided by partners from ADFG and NSB
